### 2025-03-19 background.tex
Minor modified Preliminaries chapter
fixed latex packages

\subsection{Related Work}

Formalization of mathematical theorems as proofs has been a singular research focus in modern computational mathematics. The systems such as Isabelle/HOL \cite{isabelle}, Coq \cite{bertot2013interactive}, and HOL4 \cite{slind2008brief} have been heavily relied on over the years to encode and prove basic properties but offer several features and challenges.

>>>>

\section{Related Work}

Formalization of mathematical theorems as proofs has been a singular research focus in modern computational mathematics. The systems such as Isabelle/HOL \citep{isabelle}, Coq \citep{bertot2013interactive}, and HOL4 \citep{slind2008brief} have been heavily relied on over the years to encode and prove basic properties but offer several features and challenges.
